Data and results for article
============

```{r, echo=FALSE}
dest = 'TabsAndFigs/' # where to send the figs and tables
dir.create(path=dest, 
           showWarnings = FALSE)
```

Misc. functions
------------
```{r Functions, echo=FALSE, include=FALSE}
## @knitr Init
if(!require(Hmisc))
  install.packages("Hmisc",dependencies=TRUE) # Plot error bars
if(!require(knitr))
  install.packages("knitr",dependencies=TRUE) # kable
if(!require(formatR))
  install.packages("formatR",dependencies=TRUE) # Pretty printing
if(!require(xtable))
  install.packages("xtable",dependencies=TRUE) # Output tables as latex code
if(!require(fields))
  install.packages("fields",dependencies=TRUE) # two.colors
if(!require(lmtest))
  install.packages("lmtest",dependencies=TRUE) # Linearity tests
if(!require(RColorBrewer))
  install.packages("RColorBrewer",dependencies=TRUE) # Color Sets
if(!require(robustbase))
  install.packages("robustbase",dependencies=TRUE) # Robust stats
if(!require(Rfit))
  install.packages("Rfit",dependencies=TRUE) # Robust fit
# if(!require(vioplot))
#   install.packages("vioplot",dependencies=TRUE) # Violin plots
if(!require(outliers))
  install.packages("outliers",dependencies=TRUE) # Outlier detection
if(!require(BAS)) 
  install.packages("BAS",dependencies=TRUE) # Bayesian sampling
if(!require(robcor)) 
  install.packages("robcor",dependencies=TRUE) # Robust correlations
if(!require(data.table)) 
  install.packages("data.table",dependencies=TRUE) # Tables commodities

cols=RColorBrewer::brewer.pal(8,"Set2")
cols=cbind(cols,cols)
blue_tr=rgb(unlist(t(col2rgb("blue"))),
            alpha=120,maxColorValue = 255)
red_tr=rgb(unlist(t(col2rgb("red"))),
            alpha=120,maxColorValue = 255)
green_tr=rgb(unlist(t(col2rgb("green"))),
            alpha=80,maxColorValue = 255)
orchid_tr=rgb(unlist(t(col2rgb("orchid"))),
            alpha=80,maxColorValue = 255)

myVioplot = function (datas, range = 1.5, h = NULL, 
                      ylim = NULL, names = NULL, 
                      horizontal = FALSE, col = 1:length(datas), 
                      border = "black", lty = 1, 
                      lwd = 1, rectCol = "black", 
                      colMed = "white", pchMed = 19, 
                      at, add = FALSE, wex = 1, 
                      drawRect = TRUE, side='b',...) 
{
  #   datas <- list(x, ...)
  n <- length(datas)
  if (missing(at)) 
    at <- 1:n
  upper <- vector(mode = "numeric", length = n)
  lower <- vector(mode = "numeric", length = n)
  q1 <- vector(mode = "numeric", length = n)
  q3 <- vector(mode = "numeric", length = n)
  med <- vector(mode = "numeric", length = n)
  base <- vector(mode = "list", length = n)
  height <- vector(mode = "list", length = n)
  baserange <- c(Inf, -Inf)
  args <- list(display = "none")
  if (!(is.null(h))) 
    args <- c(args, h = h)
  for (i in 1:n) {
    data <- datas[[i]]
    data.min <- min(data)
    data.max <- max(data)
    q1[i] <- quantile(data, 0.975, na.rm=TRUE)
    q3[i] <- quantile(data, 0.025, na.rm=TRUE)
    med[i] <- median(data, na.rm=TRUE)
    iqd <- q3[i] - q1[i]
    upper[i] <- min(q3[i] + range * iqd, data.max)
    lower[i] <- max(q1[i] - range * iqd, data.min)
    est.xlim <- c(min(lower[i], data.min), max(upper[i], 
                                               data.max))
    #     smout <- do.call("sm.density", c(list(data, xlim = est.xlim), 
    #                                      args))
    #     hscale <- 0.4/max(smout$estimate) * wex
    #     base[[i]] <- smout$eval.points
    #     height[[i]] <- smout$estimate * hscale
    smout <- do.call("density", args=list(data,cut=0))
    hscale <- 0.4/max(smout$y) * wex
    base[[i]] <- smout$x
    height[[i]] <- smout$y * hscale
    t <- range(base[[i]])
    baserange[1] <- min(baserange[1], t[1])
    baserange[2] <- max(baserange[2], t[2])
  }
  if (!add) {
    xlim <- if (n == 1) 
      at + c(-0.5, 0.5)
    else range(at) + min(diff(at))/2 * c(-1, 1)
    if (is.null(ylim)) {
      ylim <- baserange
    }
  }
  if (is.null(names)) {
    label <- 1:n
  }
  else {
    label <- names
  }
  boxwidth <- 0.05 * wex
  if (!add) 
    plot.new()
  if (!horizontal) {
    if (!add) {
      plot.window(xlim = xlim, ylim = ylim, ...)
      #       axis(2)
      ###       axis(1, at = at, label = label)
    }
    box()
    for (i in 1:n) {
      if( side =='b' ) {
        x = c(at[i] - height[[i]], rev(at[i] + height[[i]]))
        y = c(base[[i]], rev(base[[i]]))
        } else {
          if(side== 'l') {
            x = c(at[i] - height[[i]], rev(at[i]+ 0*height[[i]]))
            y = c(base[[i]], rev(base[[i]]))          
            } else {
              x = c(at[i]- 0*height[[i]], rev(at[i] + height[[i]]))
              y = c(base[[i]], rev(base[[i]]))
              }
          }
      polygon(x,y, col = col[i], border = border, 
              lty = lty, lwd = lwd)
      if (drawRect) {
        lines(at[c(i, i)], c(lower[i], upper[i]), lwd = lwd, 
              lty = lty)
        rect(at[i] - boxwidth/2, q1[i], at[i] + boxwidth/2, 
             q3[i], col = rectCol)
        points(at[i], med[i], pch = pchMed, col = colMed)
      }
    }
  }
  else {
    if (!add) {
      plot.window(xlim = ylim, ylim = xlim,...)
      #       axis(1)
      ###       axis(2, at = at, label = label)
    }
    box()
    for (i in 1:n) {   if( side =='b' ) {
        x = c(at[i] - height[[i]], rev(at[i] + height[[i]]))
        y = c(base[[i]], rev(base[[i]]))
        } else {
          if(side== 'l') {
            x = c(at[i] - height[[i]], rev(at[i]+ 0*height[[i]]))
            y = c(base[[i]], rev(base[[i]]))          
            } else {
              x = c(at[i]- 0*height[[i]], rev(at[i] + height[[i]]))
              y = c(base[[i]], rev(base[[i]]))
              }
          }
      polygon(y,x,
              col = col[i], border = border, 
              lty = lty, lwd = lwd)
      if (drawRect) {
        lines(c(lower[i], upper[i]), at[c(i, i)], lwd = lwd, 
              lty = lty)
        rect(q1[i], at[i] - boxwidth/2, q3[i], at[i] + 
               boxwidth/2, col = rectCol)
        points(med[i], at[i], pch = pchMed, col = colMed)
      }
    }
  }
  invisible(list(upper = upper, lower = lower, median = med, 
                 q1 = q1, q3 = q3))
}
correlMethList = function(methList,data,keep,nBoot=500,robust=FALSE) {
  
  if(robust) 
    fc = function(x) robcor(x)[1,2]
  else
    fc = function(x) cor(x,method='spearman')[1,2]
  
  y = data$exp1[keep]
  n=length(y)
  cc.med=cc.minq=cc.maxq=c()
  resu.med=resu.minq=resu.maxq=NULL

  for (meth in methList) {
    x=data[[meth]][keep]
    
    cc=c()
    for (i in 1:nBoot) {
      sub=sample.int(n,size=n,replace=TRUE)
      cc[i]= fc(cbind(x[sub],y[sub]))
    }
    cc.med[[meth]]  = fc(cbind(x,y)) #median(cc)
    cc.minq[[meth]] = quantile(cc,0.025)
    cc.maxq[[meth]] = quantile(cc,0.975)
    resu.med=rbind(resu.med,data.frame(Method=meth,cor=cc.med[[meth]],
                                 stringsAsFactors=FALSE,row.names=NULL))    
    resu.minq=rbind(resu.minq,data.frame(Method=meth,cor=cc.minq[[meth]],
                                 stringsAsFactors=FALSE,row.names=NULL))    
    resu.maxq=rbind(resu.maxq,data.frame(Method=meth,cor=cc.maxq[[meth]],
                                 stringsAsFactors=FALSE,row.names=NULL))    
  }
  return(list(med=resu.med,minq=resu.minq,maxq=resu.maxq))
}
regressMethList = function(methList,data,keep,
                           regLin=FALSE, robust=FALSE) {
  fitFunc = lm
  if(robust) fitFunc = rfit

  y = data$exp1[keep]
  reg = list()
  sdr = sdwr=c()
  resu=NULL
  for (meth in methList) {
    x=data[[meth]][keep]
    if(regLin) {
      mreg=fitFunc(y~x)
    } else {
      mreg=fitFunc(y~x+I(x^2))  
      if(!robust)
        if(anova(mreg)$Pr[2]>0.05) mreg=fitFunc(y~x)
      
    }
    
    reg[[meth]]  = mreg
    sdwr[[meth]] = sd(mreg$residuals)
    
    if(regLin) {
      resu=rbind(resu,data.frame(Method=meth,
                                 a0=mreg$coefficients[1],
                                 a1=mreg$coefficients[2],
                                 RMS=sdwr[[meth]],
                                 stringsAsFactors=FALSE,row.names=NULL)
                 )
    } else {
      resu=rbind(resu,data.frame(Method=meth,
                                 a0=mreg$coefficients[1],
                                 a1=mreg$coefficients[2],
                                 a2=(if(mreg$rank==3) mreg$coefficients[3] else 0),
                                 RMS=sdwr[[meth]],
                                 stringsAsFactors=FALSE,row.names=NULL)
                 )
    }
    
  }
  return(list(resu=resu,reg=reg))
}
looStatMethList = function (methList,data,keep,regLin,robust=FALSE) {
  yref = data$exp1[keep]
  ym=mean(yref)
  looStat=data.frame()
  for (meth in methList) {
    xref=data[[meth]][keep]
    yloo=c()
    for (iloo in 1:length(yref)) {
      y = yref[-iloo] 
      x = xref[-iloo]
      if(regLin) {
        if(robust)
          mreg=lmrob(y~x)
        else
          mreg=lm(y~x)
      } else {
        if(robust)
          mreg=lmrob(y~x+I(x^2))
        else
          mreg=lm(y~x+I(x^2))
        
        if(!robust)
          if(anova(mreg)$Pr[2]>0.05) mreg=lm(y~x)
        
      }
      yp=predict(mreg,data.frame(x=xref))
      yloo[iloo]=yp[iloo]
    }
    looStat=rbind(looStat,data.frame(Method=meth, 
                                     Q2=1-sum((yloo-yref)^2)/sum((ym-yref)^2)))
  }
  return(looStat)  
}
looPlotMethList = function (methList,data,keep,regLin,plim=c(0,1),robust=FALSE) {
  yref = data$exp1[keep]
  par(mfrow=c(nMeth/4,4),mar=c(4,4,2,0.1),cex.main=1,cex.axis=1,cex.lab=1)
  for (meth in methList) {
    xref = data[[meth]][keep]
    plot(xref,xref,xlim=c(0,max(yref)),ylim=plim,type="n", 
         xlab="Predicted Gap / eV", 
         ylab="Pred. Uncert (67%) / eV",
         main=meth)
    xp=seq(-3,30,length.out=100)
    cmin=c()
    for (iloo in 1:length(yref)) {
      y = yref[-iloo]
      x = xref[-iloo]
      if(regLin) {
        if(robust)
          mreg=lmrob(y~x)
        else
          mreg=lm(y~x)
      } else {
        if(robust)
          mreg=lmrob(y~x+I(x^2))
        else
          mreg=lm(y~x+I(x^2))
        
        if(!robust)
          if(anova(mreg)$Pr[2]>0.05) mreg=lm(y~x)
        
      }   
      yp=predict(mreg,data.frame(x=xp),interval="prediction",level=0.67)
      incr=order(yp[,1])
      lines(yp[incr,1],yp[incr,3]-yp[incr,1],col="blue",lty=1,lwd=2)
      cmin[iloo]=min(yp[,3]-yp[,1])
    }  
    #print(paste(meth,data$System[order(cmin)[1:3]],sep=":"))
  }
}
predictPlotMethList = function (methList,data,keep,reg,plim=c(0,1),cols) {  
  yref = data$exp1[keep]
  par(mfrow=c(1,1))
  x=seq(-4,30,length.out=100)
  plot(x,x,xlim=c(0,max(yref)),ylim=plim,type="n", 
       xlab="Predicted Gap / eV", ylab="Pred. Uncert (67%) / eV")
  i=0
  ltyTab=c()
  for (meth in methList) {
    i=i+1
    mreg=reg[[meth]]
    yp=predict(mreg,data.frame(x),interval="prediction",level=0.67)
    lty= 1 + 2*(i>=9)
    if(mreg$rank==3) lty=2
    ltyTab[i]=lty
    lines(yp[,1],yp[,3]-yp[,1],col=cols[i],lty=lty,lwd=2)
  }
  legend("bottomright",methList,col=cols,
         lty=ltyTab,lwd=2,ncol=4,cex=0.8,bg="white")
}
mplot= function(meth,reg,data,tag=FALSE,plim=NULL,log="",
                predictPlot=TRUE,add=FALSE,col='red') {
  mreg=reg[[meth]]
  x=data[[meth]]
  if(!add) {
    plot(x,data$exp1,col="blue",pch=20,cex=0.5,log=log,
         xlim=plim,ylim=plim,xlab="Calc.",ylab="Exp.",
         main=meth,lheight=0.5)  
    if (tag) text(x,y,data$System[keep])    
  }
  x = seq(plim[1],plim[2],length.out=100)
  y = mreg$coefficients[1] + x * mreg$coefficients[2]
  if(length(mreg$coefficients)>2) y = y + x^2 * mreg$coefficients[3]
  lines(x,y,col=col)    
  lines(x,x,col="black",lty=2)    
  
  if(predictPlot) {
    yp=suppressWarnings(predict(mreg,data.frame(x),
                                interval="prediction",level=0.67))
    lines(x,yp[,2],col=col,lty=2)
    lines(x,yp[,3],col=col,lty=2)
    }
  }
residualsPlot= function(meth,reg,data, weighted=FALSE, tag=FALSE, plim=NULL, log="") {
  mreg=reg[[meth]]
  if(weighted) {
    wres=(mreg$residuals/mreg$weights)
    ylab="Weighted residuals"
  } else {
    wres=mreg$residuals        
    ylab="Residuals / eV"
  }
  plot(mreg$model$y, wres, col="blue",pch=20,cex=0.5,
       xlab="Exp. / eV",ylab=ylab,ylim=plim,main=meth)
  if (tag) text(mreg$model$y,wres,data$System[keep],pos=4,offset=0.1)
  abline(h=0,col="black",lty=2)  
  #title(paste(meth,": St. dev.=",round(sd(wres),3)))
}
genColors = function(sample) {
  ncols=length(sample)
  co=(    sample -min(sample))/
    (max(sample)-min(sample))
  indx=round(1+(ncols-1)*co)
  cols=two.colors(ncols,start="blue",middle="white",end="red")[indx]
  return(cols)
}
# Explicit linear regression with formulae of text
wreglin = function(x,y,uy){
  n=length(x)
  
  # Define weights
  w=1/uy^2
  
  d = sum(w)*sum(w*x^2)-sum(w*x)^2
  b = (sum(w)*sum(w*x*y)-sum(w*x)*sum(w*y))/d 
  a = sum(w*y)/sum(w)-b*sum(w*x)/sum(w)
  x2= sum(w*(y-a-b*x)^2)
  if(x2 <= qchisq(0.05,df=n-2)) 
    stop(paste('exp. errors too large',x2))

  for (i in 1:5) {
    
    ud2 = max( 0,
               1 /(n-2) *sum((y-a-b*x)^2)-mean(uy^2)
             )
    
    # Redefine weights after variance partition
    w=1/(ud2+uy^2)
    
    d = sum(w)*sum(w*x^2)-sum(w*x)^2
    b = (sum(w)*sum(w*x*y)-sum(w*x)*sum(w*y))/d 
    a = sum(w*y)/sum(w)-b*sum(w*x)/sum(w)
    ub2 =  sum(w)/d
    ua2 =  sum(w*x^2)/d
    cab = -sum(w*x)/sum(w)*ub2         
  }
  
  return(list(a=a,b=b,ud2=ud2,ua2=ua2,ub2=ub2,cab=cab))
}
predlin = function(r,x) {
  a = r$a; b=r$b; ud2= r$ud2; ua2=r$ua2; ub2=r$ub2; cab=r$cab
  p   = a + b*x
  ul2 = ua2 + x^2*ub2 + 2*x*cab
  up2 = ud2 + ul2
  return(list(p=p,up=up2^0.5,ul=ul2^0.5,ratio=ul2/up2))
}
mywols=function(x,y,uy,fac=1) {
  
  r = wreglin(x,y,uy)
  
  # Mean variance and max contrib of line uncert.
  ns = 1000
  x0 = seq(min(x),max(x),len=ns)
  pr  = predlin(r,x0)
  vmean = mean(pr$up^2)
  ratio = max(pr$ratio)
    
  # Coverage score
  pr = predlin(r,x)
  vtot=mean(uy^2)+vmean
  score = sum( y>=(pr$p-fac*vtot^0.5) & y<=(pr$p+fac*vtot^0.5) )
  score = score/length(x)

  # LOO stat
  yloo=c()
  for (iloo in 1:length(y)) {
    y0 = y[-iloo] 
    x0 = x[-iloo]
    uy0= uy[-iloo]
    r0 = wreglin(x0,y0,uy0)
    yloo[iloo] = predlin(r0,x[iloo])$p
  }
  PSS = sum((y - yloo   )^2) 
  TSS = sum((y - mean(y))^2)
  Q2=1 - PSS/TSS

  return(list(a=r$a, b=r$b, ud=r$ud2^0.5, 
              vmean=vmean, ratioMax=ratio, 
              score=score, Q2=Q2,
              ua2=r$ua2, ub2=r$ub2, cab=r$cab))  
}

plot2Hist = function(data1,data2,fileName,xlab='X',ylab='Y',
                     col1='blue',col2='red',density=2,
                     breaks="Sturges",legends=c('Set 1','Set 2'),
                     legendTitle=NULL) {
  png(file=fileName,width=2400,height=1800)
  par(mfrow=c(1,1),mar=c(3,3,1,1),cex=8,lwd=6)
  ylim=c(0,max(hist(c(data1),plot=FALSE)$counts,
               hist(c(data2),plot=FALSE)$counts))
  hist(data1, breaks=breaks, freq=TRUE,col=col1,angle=45,
       density=density,
       main='',xlab='',xaxt='n',yaxt='n',ylab='',ylim=ylim)
  axis(1, at = pretty(c(data1,data2)), pos=0, padj=-0.7,lwd=4) 
  axis(2, padj=0.7, lwd=4)
  title(ylab=ylab,line=2)
  title(xlab=xlab,line=1.5)
  hist(data2, breaks=breaks,freq=TRUE,col=col2,angle=-45,
       density=density,add=TRUE) 
  abline(h=0,lwd=4)
  legend('topright', legend = legends, bty='n', title=legendTitle,
         density=density, angle = c(45,-45), fill=c(col1,col2),
         border=1)
  dev.off()  
  }

plot2Dens = function(data1,data2,fileName,col1='green',col2='orchid',
                     by='method',methList,sysList,legends=NULL,
                     x.leg='topleft',y.leg=NULL,heightFactor=1
                     ) {
  png(file=fileName,width=2400,height=2400*heightFactor)
  par(mfrow=c(1,1),mar=c(3,5.1,2,1.5),cex=8)
  ylim=range(data1)
  ll=list()
  if(by=='method') {
    for (i in 1:length(methList)) 
      ll[[i]] = data1[i,1:length(sysList)]
    names=prettyMethList    
  } else {
    for (i in 1:length(sysList)) 
      ll[[i]] = data1[1:length(methList),i]         
    names=sysList
  }
  
  myVioplot(rev(ll),col=rep(col1,length(ll)),
            drawRect=FALSE, horiz=TRUE,
            yaxt='n',ylab='',ylim=ylim,
            xaxt='n',xlab='',
            side='r',lwd=2)
  axis(1,lwd=4,padj=-0.7)
  axis(3,lwd=4,padj= 0.7)
  title(xlab= paste0('Errors on ',tolower(casesLong[ic]),
                     casesUnits[ic]),line=1.5)
  mtext(rev(paste0(names,' ')),side=2,
        at=(1:length(names))-0.5/heightFactor,las=2,
        srt=90,adj=1,padj=0,cex=8,col='black')
  
  ll=list()
  if(by=='method') {
  for (i in 1:length(methList)) 
    ll[[i]] = data2[i,1:length(sysList)]     
  } else {
  for (i in 1:length(sysList)) 
    ll[[i]] = data2[1:length(methList),i]         
  }
  myVioplot(rev(ll), col=rep(col2,length(ll)), 
            drawRect=FALSE, horiz=TRUE,
            side='l',lwd=2,add=TRUE)
  
   abline(h=1:length(names),col='gray30',lwd=2,lty=3)
#   abline(v=c(-5,0,5,10),col='gray30',lwd=2,lty=3)
  grid(ny=0,col='gray30',lwd=2,lty=3)
  abline(v=0,lwd=2)
  box(lwd=6)
  if(!is.null(legends))
    legend(x=x.leg, y=y.leg, cex=0.8,
         legend = legends, bty='y', bg='gray90',
         density = -1, fill=c(col1,col2), text.col=1)
  dev.off()  
}

```

Lecture des données 
------------
```{r DataRead, echo=FALSE}
cases      = c('band-gap','bulk-mod','latt-param')
casesLong  = c('Band gap', 'Bulk modulus','Lattice constant')
casesUnits = c(' / eV', ' / GPa',' / \uc5')
casesUexp  = c(0.01, 2.0, 0.001)

# Get data for bulk modulus: as there are only 28 systems,
# we will use them as calibration set for all methods
# The validation set (9 points) will consist of 
# the remaining data for latt-param and band-gap
case=cases[2]
data=data.frame(obs=case,uexp=casesUexp[2],
                read.table(paste0('data/',case,'_28_cub_sys.csv'),
                header=TRUE,fill=FALSE,stringsAsFactors=FALSE))
sysRefList=sort(unique(data$System))
data = setorder(data,System) 

for (i in c(1,3)) {
  case=cases[i]
  data0=data.frame(obs=case,uexp=casesUexp[i],
                   read.table(paste0('data/',case,'_37_cub_sys.csv'),
                   header=TRUE,fill=TRUE,stringsAsFactors=FALSE))
  sel   = data0$System %in% sysRefList
  data1 = subset(data0,sel)
  data1 = setorder(data1,System)  
  data  = rbind(data,data1)
  if(i==1) {
    data1 = subset(data0,!sel)
    dataVal = setorder(data1,System)  
  } else {
    data1 = subset(data0,!sel)
    data1 = setorder(data1,System)  
    dataVal = rbind(dataVal,data1)
  }  
}

colnames(data)[ncol(data)]='exp1'
colnames(dataVal)[ncol(dataVal)]='exp1'
methList=names(data)[5:(ncol(data)-1)]
prettyMethList= read.table(paste0('data/',cases[2],'_28_cub_sys.csv'),
          header=FALSE,nrows=1,stringsAsFactors=FALSE)
prettyMethList=unlist(prettyMethList[3:(length(prettyMethList)-1)])
nMeth=length(methList)
print(prettyMethList)
sysList=sysRefList
print(sort(sysList))
sysValList=sort(unique(dataVal$System))
print(sort(sysValList))

sink(file=paste0(dest,'methodsAndSystems.txt'))
cat('Methods:\n',prettyMethList,'\n\n')
cat('Calib. Sys.:\n',sysList,'\n\n')
cat('Valid. Sys.:\n',sysValList,'\n\n')
sink() 

# methColors = rainbow(nMeth)
methColors = rainbow(19,start=0.05,end=0.90)
names(methColors)=methList
sysColors = rainbow(length(sysList)+1,start=0.05,end=0.90)
```

Calculs 
------------
### Sélection du degré de régression optimal par BMC (Mana 2014)
```{r BMS, echo=FALSE}
# Define validation models to be compared
mods = c('y~1','y~0+x','y~1+x','y~1+x+I(x^2)','y~1+x+I(x^2)+I(x^3)')
dfs  = c(1,1,2,3,4) # Nb of parameters in models

modelTab=matrix(3,length(methList),length(cases))
colnames(modelTab)=cases
rownames(modelTab)=methList

for (i in 1:length(cases)) {
  par(mfrow=c(4,4),mar=c(3,2,4,0.1))
  case=cases[i]
  data0=subset(data,obs==case)
  for (meth in methList) {
    x   = data0$exp1
    y   = data0[[meth]]
    
    ym  = mean(y)
    ys  = sd(y)
    yc  = y # scale(y)
    N   = length(y)
    
    Prob=c()
    for (imod in 1:length(mods)) {
      degree=dfs[imod]
      fit = lm(as.formula(mods[imod]),data=data.frame(y=yc,x=x))
      
      yp  = fit$fitted.values
      eps = fit$residuals

      lp1 = lgamma(0.5*(N-degree)) + lgamma(0.5*degree) - 
        0.5*degree*log(sum(yp^2)) - 0.5*(N-degree)*log(t(yc)%*%eps)
      lp2 = lgamma(0.5*(N-degree)) + lgamma(0.5*N) - 0.5*N*log(sum(yp^2)) + 
        hypergeometric2F1(0.5*degree,
                          0.5*(N-degree),
                          0.5*(N-degree+2),
                          t(yc)%*%eps / sum(yp^2), 
                          method='Laplace', log=TRUE)
      Prob[imod] = exp(lp1) - exp(lp2)
      }
    Prob = Prob/sum(Prob,na.rm=TRUE)
    if(!any(is.na(Prob))) modelTab[meth,case]=which.max(Prob)
    plot(1:length(mods),Prob,type='h',col='orange',lwd=10,main=paste(meth,case),
         xlim=NULL,ylim=c(0,1),xlab='model', ylab='Probability')

    grid()
    }
  }
  modTxt=matrix(mods[modelTab],nrow=nrow(modelTab))
rownames(modTxt)=prettyMethList
colnames(modTxt)=cases
knitr::kable(modTxt,'markdown')
  sink(file='modelTable.txt')
  cat('BMC model selection\n\n')
  knitr::kable(modTxt,'markdown')
  sink() 
# WARNING : results not used : linear model (3)  assumed thereafter
# use of model 2 when most probable seems to degrade performances...

```

### Performance statistics

```{r Stats, echo=FALSE}
resid=array(0.0,
            dim=c(length(cases),length(methList),length(sysList)),
            dimnames=list(property=cases,method=methList,system=sysList)
)
residUnc=residUncAbs=resid*0.0
n=length(methList)

madTab=matrix(0.,n,length(cases))
colnames(madTab)=cases
rownames(madTab)=methList
madTabUnc = madTab
rmsTabUnc = madTab
rmsTab    = madTab
rmsUncTab = madTab
maeUncTab = madTab
rmseUncTab = madTab
mseUncTab = madTab
mseTab = madTab

for (i in 1:length(cases)) {
  case=cases[i]
  data0=subset(data,obs==case)
  keep = data0$exp1 <= max(data0$exp1)
  res=regressMethList(methList,data0,keep,regLin=TRUE)
  reg=res$reg
  for (meth in methList) resid[case,meth,]   = -reg[[meth]]$residuals
  for (meth in methList) {
    residUnc[case,meth,] = data0[[meth]]-data0$exp1
    residUncAbs[case,meth,] = abs(residUnc[case,meth,])
    }  
  maeUncTab[,i] = apply(abs(residUnc[case,,]),1,mean)
  mseUncTab[,i] = apply(residUnc[case,,],1,mean)
  mseTab[,i]    = apply(resid[case,,],1,mean)
  rmseUncTab[,i]= apply(residUnc[case,,]^2,1,mean)^0.5
  rmsUncTab[,i] = apply(residUnc[case,,],1,
                        function(x){sum((x-mean(x))^2)/length(x)} )^0.5 
  rmsTabUnc[,i] = apply(residUnc[case,,],1,sd)
  madTab[,i]    = apply(resid[case,,],1,mad)
  madTabUnc[,i] = apply(residUnc[case,,],1,mad)
  rmsTab[,i]    = apply(resid[case,,],1,
                        function(x){sum((x-mean(x))^2)/length(x)} )^0.5 
  }

```

### Linear calibration with paper's formulae + validation 

```{r LinearCalib, echo=FALSE}
ratioVar = meanPredVar = scorePred = q2Tab = 
  ua2Tab = ub2Tab = cabTab =
  aTab = bTab = udTab  =upmTab = madTab
for (i in 1:length(cases)) {
  case=cases[i]
  data0=subset(data,obs==case)
  for (meth in methList) {
    res = mywols(data0[[meth]],data0$exp1,data0$uexp)
    ratioVar[meth,case]    = res$ratioMax    
    meanPredVar[meth,case] = res$vmean
    scorePred[meth,case]   = res$score
    q2Tab[meth,case]       = res$Q2
    aTab[meth,case]        = res$a
    bTab[meth,case]        = res$b
    ua2Tab[meth,case]      = res$ua2
    ub2Tab[meth,case]      = res$ub2
    cabTab[meth,case]      = res$cab
    udTab[meth,case]       = res$ud
    upmTab[meth,case]      = res$vmean^0.5
  }
}

# knitr::kable(ratioVar,'markdown')
```

Figures & tables
------------

### III.1 Error distributions

```{r Figs_1-3, echo=FALSE}
# Fig 1
icase=3
case=cases[icase]
data0=subset(data,obs==case)
keep = data0$exp1 <= max(data0$exp1)
res=regressMethList(methList,data0,keep,regLin=TRUE)
reg=res$reg
meth = methList[6] 
xlab=paste0('Calculated ',tolower(casesLong[icase]),casesUnits[icase])

png(file=paste0(dest,'fig1Top.png'),width=2400,height=2400)
par(mfrow=c(1,1),mar=c(4.5,4.5,1,1),cex=8)
plot(data0[[meth]],data0$exp1,pch=20,col='blue',cex=0.75,lwd=4,
     xlab=xlab,ylab=paste0('Reference ',tolower(casesLong[icase]),casesUnits[icase]))
abline(a=0,b=1,lty=2,lwd=4)
abline(reg=reg[[meth]],col='orange',lwd=8,lty=1)
grid(col='gray20')
points(data0[[meth]],data0$exp1,pch=20,col='blue',cex=1)
legend('topleft',c(paste0(meth,' data'),'Regression line'), cex=0.9,
       col=c('blue','orange'),pch=c(20,-1),lty=c(0,1),lwd=8,
       title='(a)',title.adj=0.05,bty='n',inset=0.02)
box(lwd=4)
dev.off()

ylim=c(-0.05,0.21)
x=data0[[meth]]
y=data0[[meth]]-data0$exp1

png(file=paste0(dest,'fig1Bottom.png'),width=2400,height=2400)
par(mfrow=c(1,1),mar=c(4.5,4.5,1,1),cex=8)
plot(x,y,pch=20,col='blue',ylim=ylim,
     xlab=xlab,ylab=paste0('Errors ',casesUnits[icase]))
abline(reg=lm(y~x),col='orange',lwd=8)
grid(col='gray20')
points(x,y,pch=19,col='blue')
col2='blue'
abline(h=mean(y),col=col2,lwd=6)
abline(h=mean(y)-sd(y),col=col2,lwd=6,lty=2)
abline(h=mean(y)+sd(y),col=col2,lwd=6,lty=2)

col2='red'
points(data0[[meth]],-reg[[meth]]$residuals,pch=17,col='red',cex=1)
abline(h=0,col=col2,lty=1,lwd=6)
sig=rmsTab[6,icase]
abline(h=c(sig,-sig),col=col2,lty=2,lwd=6)

legend('topleft',
       c('Before correction',
         'Regression line',
         'After correction'), 
       cex=0.9,
       col=c('blue','orange','red'),pch=c(19,-1,17),
       lty=c(0,1,0),lwd=8,pt.cex=c(1,1,1),
       title='(b)',title.adj=0.05,bty='n',inset=0.02)
box(lwd=4)
dev.off()



# Fig 2
ic = 3 # LC
im = 6 # B3LYP
fileName=paste0(dest,'fig2.png')
data2 = resid[ic,im,]
data1 = residUnc[ic,im,]

plot2Hist(data1,data2,fileName,
          col1='blue',col2='red',density=2,
          breaks=seq(-0.05,0.23,0.02),
          xlab=paste0('Error on ',tolower(casesLong[icase]),casesUnits[icase]),
          ylab='Frequency',
          legends=c('Before','After'))

 
  


# Fig 3
png(file=paste0(dest,'fig3.png'),width=2400,height=1800)
icase=3
case=cases[icase]
data0=subset(data,obs==case)
data0Val=subset(dataVal,obs==case)
meth = methList[6] 

x=data0[[meth]]
y=data0$exp1
uy=data0$uexp
rr = wreglin(x,y,uy)
  
x0 = seq(min(x),7.5,len=100)
pr  = predlin(rr,x0)

par(mfrow=c(1,1),mar=c(4,4,1,0.1),cex=8)
xlab=paste0('Calculated ',tolower(casesLong[icase]),casesUnits[icase])
col2='blue'
lwd=6
plot(x,y-rr$a-rr$b*x,pch=20,col='blue',ylim=c(-0.06,0.1),xlim=c(min(x),7.5),
     xlab=xlab,ylab=paste0('Errors after correction ',casesUnits[icase]))
grid(col='gray20')
axis(1,lwd=4); axis(2,lwd=4)
points(x,y-rr$a-rr$b*x,pch=19,col='blue')
lines(x0,0*x0,col=col2,lty=1,lwd=lwd)
d=(pr$up^2-pr$ul^2)^0.5
lines(x0, pr$up,col=col2,lty=1,lwd=lwd)
lines(x0,-pr$up,col=col2,lty=1,lwd=lwd)
lines(x0, pr$ul,col=col2,lty=2,lwd=lwd)
lines(x0,-pr$ul,col=col2,lty=2,lwd=lwd)
lines(x0, d,col=col2,lty=3,lwd=lwd)
lines(x0,-d,col=col2,lty=3,lwd=lwd)
x=data0Val[[meth]]
y=data0Val$exp1-rr$a-rr$b*x
points(x,y, pch=17, col='red',cex=1)

legend('topleft',cex=0.8,pt.cex=c(1,1,1,1,1,1),
       c('Calibration set    ','Validation set    ','',
         expression(u[f]),expression(d[m]),
         expression(u[p])),
       col=c(4,2,0,col2,col2,col2),
       lty=c(0,0,0,2,3,1),
       lwd=6,
       pch=c(19,17,-1,-1,-1,-1),seg.len=1,
       bty='n', ncol=2, x.intersp=0.5)
box(lwd=4)

dev.off()

```

### IV.2 Applications / Benchmark statistics

```{r Table_II}
# Table II
tab=cbind(maeUncTab,rmseUncTab,mseUncTab,rmsUncTab)
tab=signif(tab[,c(1,4,7,10,2,5,8,11,3,6,9,12)],digits=2)
colnames(tab)=rep(c('MAE','RMSE','MSE','RMSD'),3)

knitr::kable(tab,'markdown',digits=3)

sink(file=paste0(dest,'table2.tex'))
knitr::kable(tab,'latex',digits=3)
sink()

```

### IV.3 Applications / Statistical modeling

```{r Figs_4-5}

#Figs 4 
for (ic in 1:length(cases)) {
  data1 = residUnc[ic,,]
  data2 = resid[ic,,]
  if(ic==1) 
    legends = c('Before calibration','After calibration')
  else
    legends=NULL
  
  plot2Dens(data1,data2,fileName=paste0(dest,'fig4_',cases[ic],'.png'),
            heightFactor=1.2,col1=blue_tr,col2=red_tr,
            by='method',methList=methList,sysList=sysList,
            legends = legends,
            x.leg=2.2, y.leg=13.2)
  }


# Fig 5
nm=length(methList)
png(file=paste0(dest,'fig5.png'),width=2400,height=1800)
par(mfrow=c(1,1),mar=c(5.1,3,0.1,0.1),cex=8)
matplot(1:nm,q2Tab,col=1:3,
        ylim=c(0.95,1.002),xaxt='n',xlab='',yaxs='i',
        type='n', yaxt='n', ylab='')
title(ylab='Leave One Out Statistics',line=2)
axis(2,lwd=4,padj=0.7)
mtext(paste0(prettyMethList,' '),side=1,
      at=1:length(methList),las=2,
      srt=90,adj=1,padj=0,cex=8)
grid(col='gray30')
matplot(1:nm,q2Tab,col=1:3,
        type='l',lwd=6, add=TRUE)
matplot(1:nm,q2Tab,col=1:3,
        type='p',lwd=6,pch=15:17, add=TRUE)
legend(8,0.969,cex=0.9, legend = casesLong, lty=1:3, col=1:3, 
       pch=15:17,lwd=6, bty='n')
box(lwd=4)
dev.off()

```

### IV.4 Applications / Prediction uncertainty analysis

```{r Table_III}
# Table III
tab=cbind(signif(aTab,4),
          signif(bTab,4),
          signif(udTab,2),
          signif(upmTab,2))
tab=tab[,c(1,4,7,10,2,5,8,11,3,6,9,12)]
colnames(tab)=rep(c('a','b','d','up'),3)

knitr::kable(tab,'markdown',digits=3)
sink(file=paste0(dest,'table3.tex'))
knitr::kable(tab,'latex',digits=3)
sink()

```

### IV.D.2 Applications / Prediction uncertainty / External validation

```{r Table_IV}
q2ValTab = scoreValTab = madTab
for (i in c(1,3)) {
  case     = cases[i]
  data0    = subset(data,obs==case)
  yCal  = data0$exp1
  uyCal = data0$uexp
  data0Val = subset(dataVal,obs==case)
  yVal  = data0Val$exp1
  uyVal = data0Val$uexp
  for (meth in methList) {
    # Build predictor
    xCal  = data0[[meth]]
    rCal  = wreglin(xCal,yCal,uyCal)
    pr    = predlin(rCal,xCal)

    # Validation
    xVal   = data0Val[[meth]]
    prVal  = predlin(rCal,xVal)$p
    uprVal = (predlin(rCal,xVal)$up^2 + uyVal^2)^0.5
    
    PSS = sum((yVal - prVal     )^2) 
    TSS = sum((yVal - mean(yVal))^2)
    Q2  = 1 - PSS/TSS
    q2ValTab[meth,case] = Q2
    
    sig = mywols(xCal,yCal,uyCal)$vmean^0.5
    fac = 2
    score = sum( yVal>=(prVal-fac*sig) & 
                 yVal<=(prVal+fac*sig) )
    scoreValTab[meth,case] = score
  
  }
}

# Table IV
# tab = q2ValTab[,-2]
# knitr::kable(tab,'markdown',digits=3)
# sink(file=paste0(dest,'table4Q2.tex'))
# knitr::kable(tab,'latex',digits=3)
# sink()

tab = scoreValTab[,-2]
knitr::kable(tab,'markdown',digits=3)
sink(file=paste0(dest,'table4.tex'))
knitr::kable(tab,'latex',digits=3)
sink()
```

```{r Figs_6}
# Fig 6
icase = 3
case  = cases[icase]
meth  = methList[12]
data0 = subset(data,obs==case)
yCal  = data0$exp1
uyCal  = data0$uexp
data0Val = subset(dataVal,obs==case)
yVal  = data0Val$exp1
xCal  = data0[[meth]]
rCal  = wreglin(xCal,yCal,uyCal)
prCal = predlin(rCal,xCal)$p

xVal  = data0Val[[meth]]
prVal=c()
for (iloo in 1:length(xVal))
  prVal[iloo] = predlin(rCal,xVal[iloo])$p

sig = mywols(xCal,yCal,uyCal)$vmean^0.5
fac = 2 

png(file=paste0(dest,'fig6.png'),width=2400,height=1600)
par(mfrow=c(1,1),mar=c(5.1,3,1,0.1),cex=8,lwd=6)
data1=xCal-yCal
data2=xVal-yVal
data3=prCal-yCal
data4=prVal-yVal
plot(range(c(data1,data2,data3,data4)),c(0,1),type='n',
     xlab=paste0('Error on ',tolower(casesLong[icase]),casesUnits[icase]),
     yaxt='n',ylab='')
rect(-2*sig,-05,2*sig,1.5,col='gray95',border=NA)
grid(col='gray30',lwd=2)
points(data1,data1/data1,pch=19,col='blue')
points(data2,data2/data2,pch=17,col='red')
points(data3,0*data3,pch=19,col='blue')
points(data4,0*data4,pch=17,col='red')
segments(data1,data1/data1,data3,0*data3,col='blue')
segments(data2,data2/data2,data4,0*data4,col='red')
abline(v=0,lwd=2)
mtext(c('Before ','After '),at=c(0.95,-0.02),side=2,outer=FALSE,las=2,
        srt=90,adj=1,padj=0,cex=8,col='black')
box(lwd=4)
dev.off()


```

### IV.5 Applications / Sensitivity ro reference data uncertainty

```{r Table_5, echo=FALSE}
casesUexpHighU  = c(0.3, 7.0, 0.015)

upmTabHighU = upmTab
for (i in 1:length(cases)) {
  case=cases[i]
  data0=subset(data,obs==case)
  for (meth in methList) {
    uexp=rep(casesUexpHighU[i],length(data0$exp1))
    res = mywols(data0[[meth]],data0$exp1,uexp)
    upmTabHighU[meth,case] = res$vmean^0.5
  }
}
# Table 5
tab=cbind(signif(upmTab,2),signif(upmTabHighU,2))
us=matrix(c(casesUexp,casesUexpHighU),nrow=1)
rownames(us)='us'
tab=rbind(us,tab)
tab=tab[,c(1,4,2,5,3,6)]
colnames(tab)=rep(c('up','upHighU'),3)

knitr::kable(tab,'markdown',digits=3)
sink(file=paste0(dest,'table5.tex'))
knitr::kable(tab,'latex',digits=3)
sink()

```

### IV.6 Applications / Looking back at the reference data

```{r Figs_7, echo=FALSE}

for (ic in 1:length(cases)) {
  data1 = residUnc[ic,,]
  data2 = resid[ic,,]
  plot2Dens(data1,data2,fileName=paste0(dest,'fig7_',cases[ic],'.png'),
            heightFactor=1.4,col1=blue_tr,col2=red_tr,
             by='system',methList=methList,sysList=sysList,
             legends=NULL,
             x.leg=2.2, y.leg=13.2)
  }


```

### Latex tables for Supp Mat
 
```{r Tables_SuppMat, echo=FALSE}

# Data sets
# for (case in cases) {
  case=cases[1]
  data0=subset(data,obs==case)
  knitr::kable(data0[,-1],'markdown',digits=5,row.names=FALSE)
  sink(file=paste0(dest,'tableCalib_',case,'.tex'))
  knitr::kable(data0[,-1],'latex',digits=3,row.names=FALSE)
  sink() 
  case=cases[2]
  data0=subset(data,obs==case)
  knitr::kable(data0[,-1],'markdown',digits=5,row.names=FALSE)
  sink(file=paste0(dest,'tableCalib_',case,'.tex'))
  knitr::kable(data0[,-1],'latex',digits=3,row.names=FALSE)
  sink() 
  case=cases[3]
  data0=subset(data,obs==case)
  knitr::kable(data0[,-1],'markdown',digits=5,row.names=FALSE)
  sink(file=paste0(dest,'tableCalib_',case,'.tex'))
  knitr::kable(data0[,-1],'latex',digits=3,row.names=FALSE)
  sink() 
# }
# for (case in cases[c(1,3)]) {
  case=cases[1]
  data0=subset(dataVal,obs==case)
  knitr::kable(data0[,-1],'markdown',digits=5,row.names=FALSE)
  sink(file=paste0(dest,'tableValid_',case,'.tex'))
  knitr::kable(data0[,-1],'latex',digits=3,row.names=FALSE)
  sink() 
  case=cases[3]
  data0=subset(dataVal,obs==case)
  knitr::kable(data0[,-1],'markdown',digits=5,row.names=FALSE)
  sink(file=paste0(dest,'tableValid_',case,'.tex'))
  knitr::kable(data0[,-1],'latex',digits=3,row.names=FALSE)
  sink() 
# }

# Results Tables
tab=cbind(signif(aTab,6),
          signif(bTab,6),
          signif(udTab^2,6),
          signif(ua2Tab,6),
          signif(ub2Tab,6),
          signif(cabTab,6)
          )

# for (i in 1:3) { 
  i=1
  case=cases[i]
  columns=c(1,4,7,10,13,16) + (i-1)
  tab1=tab[,columns]
  colnames(tab1)=c('a','b','d2','ua2','ub2','cab')
  sink(file=paste0(dest,'table_SM_',case,'.tex'))
  knitr::kable(tab1,'latex',digits=6)
  sink()
  i=2
  case=cases[i]
  columns=c(1,4,7,10,13,16) + (i-1)
  tab1=tab[,columns]
  colnames(tab1)=c('a','b','d2','ua2','ub2','cab')
  sink(file=paste0(dest,'table_SM_',case,'.tex'))
  knitr::kable(tab1,'latex',digits=6)
  sink()
  i=3
  case=cases[i]
  columns=c(1,4,7,10,13,16) + (i-1)
  tab1=tab[,columns]
  colnames(tab1)=c('a','b','d2','ua2','ub2','cab')
  sink(file=paste0(dest,'table_SM_',case,'.tex'))
  knitr::kable(tab1,'latex',digits=6)
  sink()
# }

```

```{r Figs_TOC}
#Fig TOC
ic=1  
data1 = residUnc[ic,,]
data2 = resid[ic,,]
plot2Dens (data1,data2,fileName=paste0(dest,'figTOC.png'),
           methList=methList,sysList=sysList,
           legends=c('Before calibration','After calibration'),
           x.leg=2.2, y.leg=13.2)


```